%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeAa}{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeAA}{\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://hridaydutta123.github.io/}{\Large Hridoy Sankar Dutta}} & Email : \href{mailto:hridoyd@iiitd.ac.in}{hridaydutta123@gmail.com}\\
  \href{http://hridaydutta123.github.io/}{http://hridaydutta123.github.io} & Mobile : +91-86381-89794\\
\end{tabular*} 

\vspace{1cm}
\textbf{Research Areas:} Social Network Analysis, Data Mining, Natural Language Processing, Graph Mining, Web Social Media.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indraprastha Institute of Information Technology}{New Delhi, India}
      {Ph.D. in Computer Science and Engineering}{July. 2017 -- Present}
    \resumeSubheading
      {National Institute of Technology, Durgapur}{West Bengal, India}
      {Master of Technology in Computer Science and Engineering;  GPA: 9.15}{May. 2015 -- May. 2017}
    \resumeSubheading
      {Institute of Science and Technology, Gauhati University}{Assam, India}
      {Bachelor of Technology in Computer Science and Engineering;  GPA: 9.17}{May. 2009 -- May. 2013}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Indian Institute of Technology, Guwahati}{Assam, India}
      {Assistant Project Engineer}{Aug. 2014 -- Apr. 2015}
      \resumeItemListStart
        \resumeItem{TTS Systems}
          {Developing Text-To-Speech systems for Assamese and Manipuri languages}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%---------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%---------------------------------------------------------------------------------------
\section{Papers under review}
(\textcolor{blue}{Conference - [C], Journal - [J]})
\resumeSubHeadingListStart
\resumeSubItem{[J]}{Udit Arora, \textbf{Hridoy Sankar Dutta}, Brihi Joshi, Aditya Chetan, Tanmoy Chakraborty. Analyzing and Detecting Collusive Users Involved in Blackmarket Retweeting Activities.}

\resumeSubItem{[C]}{Deepak Thukral, \textbf{Hridoy Sankar Dutta}, Vikram Goyal, Tanmoy Chakraborty. Catch Me if You Can: Spotting Collusive Users Involved in Blackmarket Following Services.}

\resumeSubItem{[C]}{Seongjae Choi, Kyeongpil Kang, Sungbok Shin, \textbf{Hridoy Sankar Dutta}, Tanmoy Chakraborty, Jaegul Choo and Noseong Park. Detecting Cyberattack Signals from Social Media via Label Propagation Filtering.}

\resumeSubItem{[J]}{Partha Sarathi Paul, Bishakh Chandra Ghosh, \textbf{Hridoy Sankar Dutta}, Kingshuk De, Arka Prava Basu, Prithviraj Pramanik, Sujoy Saha, Sandip Chakraborty, Niloy Ganguly, Subrata Nandi. CRIMP: Here Crisis Mapping Goes Offline.}

\resumeSubItem{[C]}{Joyita Chakraborty, Dinesh Pradhan, \textbf{Hridoy Sankar Dutta}, Subrata Nandi, and Tanmoy Chakraborty. On Good and Bad Intentions behind Anomalous Citation Patterns among Journals in Computer Sciences. arXiv preprint arXiv:1807.10804, 2018.}
\resumeSubHeadingListEnd

\section{Accepted / Published Papers}
(\textcolor{blue}{Type-A/A* conferences based on CORE ranking are highlighted in blue.})

\resumeSubHeadingListStart
\resumeSubItem{[C]}{\textbf{Hridoy Sankar Dutta}, Aditya Chetan, Brihi Joshi, Tanmoy Chakraborty. CoReRank: Ranking to Detect Users Involved in Blackmarket-based Collusive Retweeting Activities. \textit{\textcolor{blue}{12th ACM International Conference on Web Search and Data Mining (WSDM)}}, Melbourne, Australia, Feb 11-15, 2019. (Acceptance rate: 16\%)}


\resumeSubItem{[C]}{\textbf{Hridoy Sankar Dutta}, Aditya Chetan, Brihi Joshi, Tanmoy Chakraborty. Retweet Us, We Will Retweet You: Spotting Collusive Retweeters Involved in Blackmarket Services, \textit{IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining} (ASONAM), Barcelona, Spain, Aug 28-31, 2018.} (Acceptance rate: 15\%)

\resumeSubItem{[C]}{Partha Sarathi Paul, \textbf{Hridoy Sankar Dutta}, Bishakh Chandra Ghosh, Krishnandu Hazra, Sandip Chakraborty, Sujoy Saha, Subrata Nandi. Offline crisis mapping by opportunistic dissemination of crisis data after large-scale disasters, \textit{\textcolor{blue}{2nd ACM SIGSPATIAL International Workshop on the Use of GIS in Emergency Management}}, California, United States, Oct 31-Nov 3, 2016.}

\resumeSubItem{[C]}{Sandip Chakraborty, Suchetana Chakraborty, Sushanta Karmakar, \textbf{Hridoy Sankar Dutta}. Hierarchical topology adaptation for distributed convergecast applications, In \textit{29th Annual ACM Symposium on Applied Computing}, Gyeongju, Korea, March 24-28, 2014.}

\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	Selected Projects Section
%----------------------------------------------------------------------------------------
\section{Selected Projects}
All projects are available on git : \url{https://www.github.com/hridaydutta123}
%\setlist[itemize]{
\resumeSubHeadingListStart
 \resumeSubItem{[$P_1$]}{\textbf{Collusive User Detection Tool}:A tool for detection of collusive users in Online Social Networks.}
 \resumeSubItem{[$P_2$]}{\textbf{Awesome Twitter Tools}: A curated list of tools, datasets, research papers and browser extensions related to Twitter.}
 \resumeSubItem{[$P_3$]}{\textbf{Opportunistic Network for Android Application}: Implementation of Communication Medium for Challenge Network Scenario.}
 \resumeSubItem{[$P_4$]}{\textbf{Offline Master Control Station}:Implementation of reliable and effective data transfer from oppurtunistic network and tool for analyzing behaviour of data captured in Oppurtunistic Networks.}
 \resumeSubItem{[$P_5$]}{\textbf{Designing TTS System in Assamese and Manipuri Languages}: It involves building systems for synthesizing natural speech in native Assamese and Manipuri tone from a given text and building user friendly GUIs for the common people.}
 \resumeSubItem{[$P_6$]}{\textbf{MapDisarm}:Offline efficient transfer of OSM Map tiles among various devices without internet connectivity for gps based recovery in Oppurtunistic network.}

\resumeSubHeadingListEnd

%----------------------------------------------------------------------------------------
%	ACHIEVEMENT SECTION
%----------------------------------------------------------------------------------------
\section{Achievements and Awards}
\resumeSubHeadingListStart
  \resumeSubItem{[$A_1$]}{Awarded Student Travel Grant to attend CODS COMAD 2019.}
 \resumeSubItem{[$A_2$]}{Grand Challenge Grade \textbf{A} winner where smart \& embedded device innovators around the world vied for the top spot. Organised by International Symposium Embedded Devices, 2016 at IIT Patna.}
 \resumeSubItem{[$A_3$]}{Came \textbf{1st Runners Up} in Startup Weekend, Kolkata (5-7th August, 2016).}
 \resumeSubItem{[$A_4$]}{Media Coverage of our Group in a local daily:\textit{Aamarkatha}}
 \resumeSubItem{[$A_5$]}{Won \textbf{3rd Prize in Coding Competition} at Techniche 2012 (IIT Guwahati Technical Fest Coding Event).}
 \resumeSubItem{[$A_6$]}{Attended NASSCOM Product Conclave-2016 as Student Researcher of ForkIT}
 \resumeSubItem{[$A_7$]}{Rank of \textbf{3} in Master Of Technology.}
 \resumeSubItem{[$A_8$]}{Secured 10/10 SGPA in M.Tech(3rd \& 4th Semester)}
 \resumeSubItem{[$A_9$]}{Secured 10/10 SGPA in B.Tech(6th,7th \& 8th Semester)}
 \resumeSubItem{[$A_{10}$]}{GATE Qualified (2016) – \textbf{Gate Score : 488 (Rank: 4370)}}
 \resumeSubItem{[$A_{11}$]}{GATE Qualified (2015) – \textbf{Gate Score : 441 (Rank: 6675)}}
 \resumeSubItem{[$A_{12}$]}{Passed “A” level examination of National Cadet Crops (NCC)}
\resumeSubHeadingListEnd



%----------------------------------------------------------------------------------------
%	ATTENDED EVENTS SECTION
%----------------------------------------------------------------------------------------
\section{Events \& Workshops Attended}
\resumeSubHeadingListStart
 \resumeSubItem{[$E_{1}$]}{Amazon Research Days, Bangalore (2018)}
  \resumeSubItem{[$E_{2}$]}{Young Scientist Conference at India International Science Festival (2018)}
 \resumeSubItem{[$E_{3}$]}{Workshop on Complex and Social Networks, IIT Kharagpur (2017)}
 \resumeSubItem{[$E_{4}$]}{NASSCOM Product Conclave, Bangalore (2016)}
\resumeSubHeadingListEnd


\section{Technical Skills}
\textbf{Strongest Areas} - Social Network Analysis, Natural Language Processing, Data Mining, Machine Learning, Data Structures \& Algorithms, Web Technology, System Programming \\
\textbf{Languages} - Python, Java, PHP, C++, UNIX Shell, HTML, CSS, JS, Ajax, Perl \\
\textbf{Frameworks} - Twitter API Clients, NLTK, Sklearn, Gensim, Django, Flask, Phonegap \\
\textbf{Tools} - Git, Android Studio, Adobe Photoshop, JUnit, \LaTeX \\
\textbf{Databases} - MySQL, SQLite, MongoDB \\

\section{References}
\resumeSubHeadingListStart
\item[] \textbf{Dr. Tanmoy Chakraborty} \textless \href{mailto:tanmoy@iiitd.ac.in}{tanmoy@iiitd.ac.in}\textgreater, Asst. Professor, Dept. of CSE, IIIT Delhi
\item[] \textbf{Dr. Sandip Chakraborty} \textless \href{mailto:sandipc@cse.iitkgp.ac.in}{sandipc@cse.iitkgp.ac.in}\textgreater, Asst. Professor, Dept. of CSE, IIT Kharagpur
\item[] \textbf{Dr. Subrata Nandi} \textless \href{mailto:subrata.nandi@cse.nitdgp.ac.in}{subrata.nandi@cse.nitdgp.ac.in}\textgreater, Assoc. Professor, Dept. of CSE, NIT Durgapur
\item[] \textbf{Dr. Bibhash Sen} \textless \href{mailto:bibhash.sen@cse.nitdgp.ac.in}{bibhash.sen@cse.nitdgp.ac.in}\textgreater, Assoc. Professor, Dept. of CSE, NIT Durgapur
\resumeSubHeadingListEnd
\end{document}
